An Improved ANS Transaction Template

### 2018-01-26 paper.tex
adding some figures

@@

\section{Results}

\subsection{wWithout tail recycling}
Despite the reconfiguration of each level occuring in the second case, the case
1 is way more effective to produce HEU than case 1.
Indeed as observed on Figure \ref{} and \ref{}, the first case is able to
produce a an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.
This is the consequence of the usage of un-touched cascade in the case 1:
because the cut value at each stage is unchanged it artificially produces over
enricht tails when feeded with higher enriched materials compared to a cascade
feed with the same feed assay but with a cascade designed for it.
The effective cut values for each cascade can be computed as :
\begin{equation}\label{eq:theta_eff}
    \theta = \dfrac{N - N''}{N'-N''}
\end{equation}

@@

\subsection{Assays}
\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade level
required to enrich the uranium up to $90\%$ are respectively 5 for the
first case considered. Recycling the tails, allow to reduce the number of
enrichment levels required to enrich natural uranium up to a high enrich level
to 3.

>>>>

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.7]{flow_case_2_recy.pdf}
  \caption{Illustraction of the different cascade level materials flow with tail
  recycling.}
  \label{fig:flow}
\end{figure}

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occuring in the second case, the case
1 is way more effective to produce HEU than case 1.
Indeed as observed on Figure \ref{} and \ref{}, the first case is able to
produce a an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.
This is the consequence of the usage of un-touched cascade in the case 1:
because the cut value at each stage is unchanged it artificially produces over
enricht tails when feeded with higher enriched materials compared to a cascade
feed with the same feed assay but with a cascade designed for it.
The effective cut values for each cascade can be computed as :
\begin{equation}\label{eq:theta_eff}
    \theta = \dfrac{N - N''}{N'-N''}
\end{equation}

@@

\subsubsection{tails recycling}
\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade level
required to enrich the uranium up to $90\%$ are respectively 5 for the
first case considered. Recycling the tails, allow to reduce the number of
enrichment levels required to enrich natural uranium up to a high enrich level
to 3.
